### 2011-03-30 Review/answers.tex
Finished revisions. Waiting a reply from Jos.

\begin{document}
\textbf{Question:}
\begin{quotation}
The main quantity that the paper focuses on is the thickness of the film between the bubbles and the
wall. As shown by Figure 8 and as mentioned by the Authors in Section 4, the film thickness varies
along the bubble. However, the Authors do not explain the choice of the location of the measurement
of the film thickness. This choice is of primary importance when comparing results with those of
the
literature and in particular with works on finger propagation in which the film thickness is
measured
”at infinity”.
\end{quotation}

\textbf{Answer:} The following section is added to the text 
\begin{quotation}
We chose to measure the film thickness in the middle of the bubble. The
classical Bretherton formulation is for the measurement of the film thickness at ``infinity''.
However, \citet{cerro-bubble-train} indicate that for the gravity-driven bubble train flow in tubes
it is enough for bubble to have a length of two-three diameters to apply analysis for very long
bubbles. In comparison with the axisymmetric circular geometry, for three-dimensional square shaped
microchannels \citet{heil-threedim} indicate the measurement of the film thickness at $5.5$
channel heights from the front bubble tip. This distance was shown sufficient for the
film thickness to establish itself for the capillary number range $Ca<4$. We chose to measure
the film thickness in the middle of the bubble, which is located at least at the distance of $2.5-3$
channel heights from the front bubble tip.  Moreover, the film thickness examination, see Section
\ref{section:film:thickness:variation}, shows that for the capillary range of interest, i.e.
$0.08\leq Ca \leq 1$, the standard deviation from the bubble middle film thickness is around $7$
 percent for small capillary numbers ($Ca=0.05$) and less than $1$ percent for larger ones
($Ca \geq 0.1$) at the distances ranging from one channel height from the rear tip upto one channel
height to the front tip. This certainly validates the point of choice to measure bubble thickness.
\end{quotation}

@@

\texbf{Answer:} We thoroughly corrected all the inconsistencies.

@@

\textbf{Answer:} We added additional section which shows the change of flow pattern.

@@

>>>>

\begin{document}
\section{Reviewer I}

\textbf{Question:}
\begin{quotation}
The authors found that quite surprisingly at high viscosity ratio, the results are
independent of any inertial effects. It is known that Lattice Boltzmann has some problem for high
viscosity ratio binary fluids. It will be better if the authors provide some details how the high
viscosity ratio is tackled in their LB code.
\end{quotation}

\textbf{Answer:} The reviewer is right that accuracy of the method deteriorate with the high
viscosity ratio. However, the parameters we chose here as $\tau_{\mathrm{liq}}=3.5-7.5$ and with
grids in the vertical direction as $N_y=202$ is sufficient to suppress effects. We have added all
the necessary references in the text.

\textbf{Question:}
\begin{quotation}
Figure 8 needs to redrawn. Also, there are some inconsistencies in other figures. Authors may
want to review all the figures and ensure that they have uniform fonts, etc.
\end{quotation}

\textbf{Answer:} We redrawed all the curves. For the figure 8 the data was extracted from the
figure and rescaled for the comparison reasons.

\section{Reviewer II}

\textbf{Question:}
\begin{quotation}
The main quantity that the paper focuses on is the thickness of the film between the bubbles and the
wall. As shown by Figure 8 and as mentioned by the Authors in Section 4, the film thickness varies
along the bubble. However, the Authors do not explain the choice of the location of the measurement
of the film thickness. This choice is of primary importance when comparing results with those of
the
literature and in particular with works on finger propagation in which the film thickness is
measured
”at infinity”.
\end{quotation}

\textbf{Answer:} The following section is added to the text 
\begin{quotation}
We chose to measure the film thickness in the middle of the bubble. The
classical Bretherton formulation is for the measurement of the film thickness at ``infinity''.
However, \citet{cerro-bubble-train} indicate that for the gravity-driven bubble train flow in tubes
it is enough for bubble to have a length of two-three diameters to apply analysis for very long
bubbles. In comparison with the axisymmetric circular geometry, for three-dimensional square shaped
microchannels \citet{heil-threedim} indicate the measurement of the film thickness at $5.5$
channel heights from the front bubble tip. This distance was shown sufficient for the
film thickness to establish itself for the capillary number range $Ca<4$. We chose to measure
the film thickness in the middle of the bubble, which is located at least at the distance of $2.5-3$
channel heights from the front bubble tip.  Moreover, the film thickness examination, see Section
..., shows that for the capillary range of interest, i.e.
$0.08\leq Ca \leq 1$, the standard deviation from the bubble middle film thickness is around $7$
 percent for small capillary numbers ($Ca=0.05$) and less than $1$ percent for larger ones
($Ca \geq 0.1$) at the distances ranging from one channel height from the rear tip upto one channel
height to the front tip. This certainly validates the point of choice to measure bubble thickness.
\end{quotation}

@@

\textbf{Answer:} We thoroughly corrected all the inconsistencies.

@@

\textbf{Answer:} We added an additional paragraph which shows the change of flow pattern for the
streamlines as it is indicated in literature.

@@

\textbf{Answer:} We added additional information about results to the corresponding sections. The
pressure drop are not measured as they are influenced largely by Reynolds number which is beyond
the scope of this work.

\textbf{Question:}
\begin{quotation}
The Authors mention the shooting method. It is not clear if this method is really used or just
mentioned as a part of the discussion.
\end{quotation}

\textbf{Answer:} This is a part of discussion to have a remedy for the velocity. The corresponding
sentence is added.

\textbf{Question:}
\begin{quotation}
It seems more appropriate to introduce the variables of the Bretherton’s problem as well as to plot
Figure 1 elsewhere than in the Section ”Results”.
\end{quotation}

\textbf{Answer:} The corresponding figure for the classical Bretherton problem is added. We
separate it from the numerical benchmark layout.

\textbf{Question:}
\begin{quotation}
Minor corrections...
\end{quotation}

\textbf{Answer:} All the corrections are taken into the account.
